Leaf traits drive differences in biomass partitioning among major plant functional types

### 2014-12-15 manuscript.Rnw
Updated Table S1, replaces S1 and S2 - much more consistent with Table 1 (which has also been updated a bit)

\author[1]{Remko A. Duursma}
\author[2]{Daniel S. Falster}
\author[3]{BAAD contributors}

@@

<<results='asis'>>=
print(xtable(table_gamr2MIgdd0, label="table/gamr2table",
      caption="Explained variance by plant functional type (PFT), plant height (H), moisture index (MI) and growing season average temperature (mgdd0), for six whole-plant variables. Each variable was added as a smooth term in a generalized additive model, with the exception of PFT (a categorical variable)."), caption.placement="top")
@

<<results='asis'>>=
print(xtable(table_varpart2, label="varpartpipe",
             caption="Explained variance in the ratio of leaf mass to basal stem area, and leaf area to basal stem area. The R2 shown is that explained by the fixed effects only (H = plant height, B = biome, PFT = plant functional type.  All fixed effects were highly significant (P \\textless 0.001). In addition to the fixed effects shown, all interactions were added to each of the models."),
      include.rownames=FALSE, caption.placement="top")
@

@@

<<results='asis'>>=
print(xtable(dataauthors,
             caption="Contributors to the BAAD"
             ), include.rownames=FALSE, tabular.environment='longtable', floating=FALSE, size="small",
      caption.placement="top")
@

@@

>>>>

\author[1]{Remko A. Duursma}
\author[2]{Daniel S. Falster}
\author[3]{the BAAD consortium}

@@

<<results='asis'>>=
print(xtable(table_gamr2MATMAP, label="table/gamr2table",
      caption="Explained variance by plant functional type (PFT), plant height (H), mean annual temperature (MAT) and mean annual precipitation (MAP), for five whole-plant variables. Each variable was added as a smooth term in a generalized additive model, with the exception of PFT (a categorical variable)."), 
      include.rownames=FALSE, caption.placement="top")
@

@@

<<results='asis'>>=
print(xtable(dataauthors,
             caption="Co-authors in the BAAD consortium."
             ), include.rownames=FALSE, tabular.environment='longtable', floating=FALSE, size="small",
      caption.placement="top")
@

@@

<<results='asis'>>=
print(xtable(table_varpart2, label="varpart2",
             caption="Explained variance in the ratio of leaf mass to basal stem area, and leaf area to basal stem area. The R2 shown is that explained by the fixed effects only (H = plant height, B = biome, PFT = plant functional type.  All fixed effects were highly significant (P \\textless 0.001). In addition to the fixed effects shown, all interactions were added to each of the models."),
      include.rownames=FALSE, caption.placement="top")
@
